---
title: "Hepatitis C Virus Clustering via K-Means"
author: "Rex Manglicmot"
output: 
  github_document: 
    toc: yes
---

## Status: Continuing Working Document


## Introduction


The target attribute for classification is Category (blood donors vs. Hepatitis C (including its progress ('just' Hepatitis C, Fibrosis, Cirrhosis).

All attributes except Category and Sex are numerical. The laboratory data are the attributes 5-14.

1) X (Patient ID/No.)
2) Category (diagnosis) (values: '0=Blood Donor', '0s=suspect Blood Donor', '1=Hepatitis', '2=Fibrosis', '3=Cirrhosis')
3) Age (in years)
4) Sex (f,m)
5) ALB
6) ALP
7) ALT
8) AST
9) BIL
10) CHE
11) CHOL
12) CREA
13) GGT
14) PROT


## Loading the Libraries
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(ggthemes)

```



## Loading the Data
```{r}
#laod data into an url object
url <- ('https://archive.ics.uci.edu/ml/machine-learning-databases/00571/hcvdat0.csv')

#put data into an object
data_orig <- read.csv(url)

#view strucuture
str(data_orig)
```

## Cleaning the Data
```{r}
#make copy for cleaning
data <- data_orig

#view any NAs
sum(is.na(data))

#which rows have NAs
which(is.na(data), arr.ind = TRUE)
```


```{r}
#clean data all in one go
data <- data %>%
  #get rid of variables that are not needed for Kmeans via dplyr
  select(-c(X, Category, Sex)) %>%
  #rename columns to lower case
  rename_all(tolower) %>%
  #deletes NAs
  drop_na()
```

Let's Explore

## Exploratory Data Analysis
```{r}
#show summary statistics of data
summary(data)
```


```{r}
ggplot(gather(data, cols, value), aes(x = value, fill=cols)) + 
       geom_histogram(binwidth = 1) + 
  facet_wrap(.~cols, scales = 'free') + 
  theme_calc() +
  scale_fill_brewer(palette="Paired")
```

```{r}
ggplot(gather(data, cols, value), aes(x = value, fill=cols)) + 
  geom_boxplot() + 
  facet_wrap(.~cols, scales = 'free') + 
  theme_calc() +
  scale_fill_brewer(palette="Paired") 
```

```{r}
ggplot(gather(data, cols, value), aes(x = value, fill=cols)) + 
  geom_density() + 
  facet_wrap(.~cols, scales = 'free') + 
  theme_calc() +
  scale_fill_brewer(palette="Paired") 
```


## K-Means



```{r}

```


## Limitations




## Conclusion


## Inspirationn for this project
